### 2014-07-03 research/paper/main/article.tex
spectum plots

 It is expected that vortex shedding will be well correlated along the span and provide significant forcing at low \reynoldsnumber. \citet{Joly2012} introduced  an additional sinusoidal forcing function to the hydrodynamic forcing to model this. This enables the model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present. In this study, the forcing due to vortex shedding in low \reynoldsnumber\ cases is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the right-hand side of equation \ref{equationofmotion}. Here, $\omega_{s}$ and $F_0$ represent the angular vortex shedding frequency and the maximum force due to shedding respectively. Thus, the final equation for the modified QSS model is

\begin{equation}
\label{final_equation_motion}
m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}.
\end{equation}

@@

\subparagraph{limitation of the quasi-steady hypothesis at low Reynolds numbers}

Work done by \cite{Joly2012} has also been focused on the displacement of a body under galloping at low Reynolds numbers as well as at zero or minimal damping. Therefore studies were carried out analyse the behaviour of the velocity as the damping is increased. The quasi-steady results were compared with the DNS results. From the comparison it was found out that the discrepancy of the power output is quite high as \massdamp is increased.

 \input{../figure/spectrum_pi_1_10}

>>>>

 It is expected that vortex shedding will be well correlated along the span and provide significant forcing at low \reynoldsnumber. \citet{Joly2012} introduced  an additional sinusoidal forcing function to the hydrodynamic forcing to model this. This enables the model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present. However, in this study we also focus on isolating the regions where the QSS model predicts well and therefore the additional sinusoidal forcing function is disregarded.

\begin{equation}
\label{final_equation_motion}
m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7}.
\end{equation}%

@@

\subsection{limitations of the quasi-steady hypothesis at low Reynolds numbers}

\cite{Joly2012} showed that the displacement data obtained using the QSS assumption and DNS agree well at low Reynolds numbers, with the modification implemented to the oscillator equation which accounts for the vortex shedding. These data were obtained at zero damping levels. Since the current study was focused on the power transfer, more focus was put on analyzing he behaviour od the velocity as the damping is increased. The comparison between the QSS and the DNS results revealed that the discrepancy of the power data  increases significantly as \massdamp \ is increased. From figure \ref{fig:spectrum_pi1_10} (powers spectrum analysis done on the DNS results) it is evident that the relative strength of the galloping signal decreases as the \massdamp \ is increased from $ 0 \rightarrow 0.7$. Therefore the influence of the vortex shedding becomes more significant and the interactions between galloping and shedding become more complex as the damping is increased.

 \input{../figure/spectrum_pi_1_10}
 \input{../figure/power_data}
